### 2022-05-27 sections/conferences-full.tex
Update conferences-full.tex

\begin{benumerate}{69}

@@

>>>>

\begin{benumerate}{71}

@@

\item{\small González-Bustamante, B. (2022). {\itshape Ministerial Stability During Presidential Approval Crises: Evidence from Brazil and Chile}. Presentation delivered at the Political Studies Association Early Career Network Annual Conference, Sheffield, UK.}\vspace{1mm}

\item{\small González-Bustamante, B. (2022). {\itshape Time-Dependent Data Encoding and Time-Varying Exposure Survival Models to Study Presidential Crises}. Presentation delivered at the R User Conference 2022, Virtual.}\vspace{1mm}
